\section{Week 2}
\subsection{1/12/2020}
\begin{itemize}
    \item For multiplication, the entry in row $i$ column $j$ is the dot of row $i$ of A and column $j$ of B.
    \item Distributed from the left and right
    \item Associative
    \item Suppose A is a square matrix. $A^{-1}$ is a matrix of the same such that:
    \item $AI = IA = A$
    \item $A^{-1}A=AA^{-1}=I$
    \item An inverse matrix may not exist if
    \begin{itemize}
        \item not square
        \item if any row is a linear combination of other rows
    \end{itemize}
    \item If an inverse matrix exists, it is really helpful to solve a system of equations.
    \item A $2\times 2$ matrix is invertible if and only if $ad-bc$, the determinant, is not zero. In this case, we find the inverse of a 2x2 matrix.
    $$A=\begin{bmatrix}a&b\\c&d\end{bmatrix}$$
    $$A^{-1}=\frac{1}{|A|}\begin{bmatrix}d&-b\\-c&a\end{bmatrix}=\frac{1}{ad-bc}\begin{bmatrix}d&-b\\-c&a\end{bmatrix}$$
    \item A diagonal matrix of any size is invertible when none of the diagonal entries are zero.
    \item If they are invertible $(AB)^{-1} = B^{-1}A^{-1}$
    \item Any matrix that causes a known change, should be easy to invert. We have to think of a matrix that would undo what is done.
    Ex. $$E=\begin{bmatrix}1&0&0\\-5&1&0\\0&0&1\end{bmatrix}$$ subtracts 5 times row1 from row2
    \item So we would want something that adds 5 times row1 to row2
    Result:
    $$E=\begin{bmatrix}1&0&0\\5&1&0\\0&0&1\end{bmatrix}$$
    \item $$P^{-1} = P^{12} = \begin{bmatrix}0&1&0\\1&0&0\\0&0&1\end{bmatrix}$$
    \item When the inverse is not immediately obvious, one method of calculating it is called the Gauss-Jordan method. This is done by.
    \begin{enumerate}
        \item Putting the matrix you wish to invert next to the identity matrix
        \item Use row transformations (elimination) to transform your matrix into the identity.
        \item The identity will have been transformed into the inverse matrix.
    \end{enumerate}
    \item Ex. $$A=\begin{bmatrix}2&-1&0&1&0&0\\-1&2&-1&0&1&0\\0&-1&2&0&0&1\end{bmatrix}$$
    \item $2R_2+R_1$
    $$A=\begin{bmatrix}2&-1&0&1&0&0\\0&3&-2&1&2&0\\0&-1&2&0&0&1\end{bmatrix}$$
    \item $3R_3+R_2$
    $$A=\begin{bmatrix}2&-1&0&1&0&0\\0&3&-2&1&2&0\\0&0&4&1&2&3\end{bmatrix}$$
    \item $2R_2+R_3$
    $$A=\begin{bmatrix}2&-1&0&1&0&0\\0&6&0&3&6&3\\0&0&4&1&2&3\end{bmatrix}$$
    \item $6R_1+R_2$
    $$A=\begin{bmatrix}12&0&0&9&6&3\\0&6&0&3&6&3\\0&0&4&1&2&3\end{bmatrix}$$
    $$A=\begin{bmatrix}12&0&0&9&6&3\\0&6&0&3&6&3\\0&0&4&1&2&3\end{bmatrix}\begin{bmatrix}\frac{1}{12}\\\frac{1}{6}\\\frac{1}{4}\end{bmatrix}=\begin{bmatrix}1&0&0&3/4&1/2&1/4\\0&1&0&1/2&1&1/2\\0&0&1&1/4&1/2&3/4\end{bmatrix}$$
\end{itemize}

\subsection{1/13/2021}
\begin{itemize}
    \item We are trying to factorize for the lower and upper triangular matrices.
    \item Ex. $\begin{bmatrix}1&0\\-3&1\end{bmatrix}\begin{bmatrix}2&1\\6&8\end{bmatrix}=\begin{bmatrix}2&1\\0&5\end{bmatrix}$
    \item every $E^{-1}_{ij}$ matrix is lower triangular, with 1's on the main diagonal. The off diagonla entry is +k to undo the elimination done by the - k when multiplied from the left by $E_{ij}$
    \item The product of several elimination matrices is still lower triangular.
\end{itemize}